Packaging research artifacts with RO-Crate

### 2021-05-03 latex/ro-crate.tex
markdown as well in ../output
include all markdown files
authors

% PLEASE USE THIS FILE AS A TEMPLATE
% Check file iosart2x.tex for more examples

% add. options: [seceqn,secthm,crcready]
\documentclass[ds]{iosart2x}
\usepackage[smartEllipses]{markdown}

@@

%\pretitle{}
\title{Article title}
\runtitle{Running head title}
%\subtitle{}

@@

% Two or more authors:
\author[A]{\inits{N.}\fnms{Name1} \snm{Surname1}\ead[label=e1]{first@somewhere.com}\ead[label=o1,orcid]{0000-0000-0000-0001}%
\thanks{Corresponding author. \printead{e1}.}},
\author[B]{\inits{N.N.}\fnms{Name2 Name2} \snm{Surname2}\ead[label=e2]{second@somewhere.com}\ead[label=o2,orcid]{0000-0000-0000-0002}}
and
\author[C]{\inits{N.-N.}\fnms{Name3-Name3} \snm{Surname3}\ead[label=e3]{third@somewhere.com}\ead[label=o3,orcid]{0000-0000-0000-0003}}
\address[A]{Department first, \orgname{University or Company name},
Abbreviate US states, \cny{Country}\printead[presep={\\}]{e1,o1}}
\address[B]{Department first, \orgname{University or Company name},
Abbreviate US states, \cny{Country}\printead[presep={\\}]{e2,o2}}
\address[C]{Department first, \orgname{University or Company name},
Abbreviate US states, \cny{Country}\printead[presep={\\}]{e3,o3}}

@@

\begin{keyword}
\kwd{Keyword one}
\kwd{keyword two}
\end{keyword}

@@

\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/30.formal-definition.md}

>>>>

%% ro-crate paper
%% (c) 2020-2021 The University of Manchester
%% 
%% SPDX-License-Identifier: CC-BY-4.0

% add. options: [seceqn,secthm,crcready]
\documentclass[ds]{iosart2x}
\usepackage[smartEllipses]{markdown}
\def\markdownOptionOutputDir{../output}

%\markdownSetup{
%    defaultOptions.cacheDir = 
%}

@@

%\pretitle{}
\title{Packaging research artifacts with RO-Crate}
\runtitle{Packaging research artifacts with RO-Crate}
%\subtitle{}

@@

% Two or more authors:
\author[A]{\inits{S.S-R.}\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[B]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}}
and
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}}
\author[C]{\inits{P.G.}\fnms{Paul} \snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e2,o2}}
\address[C]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e3,o3}}

@@

\begin{keyword}
\kwd{Data publishing}
\kwd{Data packaging}
\kwd{FAIR}
\kwd{Linked Data}
\kwd{Metadata}
\kwd{Reproducibility}
\kwd{Research Object}
\end{keyword}

@@

\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
%\markdownInput{../content/80.formal-definition.md}
